Number recognition for use in a Sudoku solver

### 2012-03-15 doc/icml2010stylefiles/paper.tex

\section{Introduction}
Number and letter recognition is key in many real-world applications. Digitalizing print media, automated sorting of letters, or recognition of signs in robotics or driver assistance systems require well performing algorithms for character recognition. In the following we analyze the performance of different techniques for number recognition, namely Neural Networks, Support Vector Machines and Logistic Regression, by using them in an automated sudoku solver.

@@

\section{Generation of Training Data}
\subsection{Image Generation}
\begin{figure}[ht]
	\centerline{\includegraphics[scale=0.25]{examples}}
	\caption{Examples of generated numbers}
	\label{fig:generated_numbers}
\end{figure}

\subsection{Image Processing}

>>>>

\section{Introduction}
Number and letter recognition is key in many real-world applications. Digitalizing print media, automated sorting of letters, or recognition of signs in robotics or driver assistance systems require well performing algorithms for character recognition. In the following we analyze the performance of different techniques for number recognition, namely Neural Networks, Support Vector Machines and Logistic Regression, by using them in an automated Sudoku solver.

@@

\section{Generation of Training Data}
\subsection{Image Generation}
\begin{figure}[ht]
	\centerline{\includegraphics[scale=0.25]{examples}}
	\caption{Examples of generated numbers}
	\label{fig:generated_numbers}
\end{figure}
\subsection{Image Processing}
